---
title: "Data exploration of LFS armenian data"
author: "MS4"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: tactile #cayman
    highlight: github
    toc: true
    toc_depth: 5
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo = FALSE}
packs <- c("xlsx","dplyr","tidyr","sdcMicro","archive")

p <- sapply(packs, install.packages)
p <- lapply(packs,function(p) suppressPackageStartupMessages(library(p,character.only = TRUE)))
rm(p)
# rm(list=ls())
```

### Prepare data :

```{r}

download.file(
  destfile = "data/lfs_micro_arm_2020.7z",
  url = "https://www.armstat.am/file/doc/99528268.7z"
)
archive::archive_extract("data/lfs_micro_arm_2020.7z",dir = "data/")
# To read it 
lfs_micro_arm_2020 <- haven::read_spss("data/LFS_2020_2020 Dataset_Residents.sav")

lfs_micro_arm_2020 <-
  lfs_micro_arm_2020 %>% 
  mutate(
    id_hh = as.numeric(substr(IDmem,1,nchar(IDmem)-2)), # concatenation of month + questionnaire_num
    id_indiv = substr(IDmem,nchar(IDmem)-1,nchar(IDmem))
  ) 

```

Household identification :

A6_month : month of survey
A1 : questionnaire number

Quasi-identifying variables :

- B5, B6 : Date of birth
- B3 : Gender
- A3 : Geographical Area (Marz)
- B11 : Marital Status 
- B7 : Diploma

Sensitive variables 

- E15 : Income
- C2 : country of citizenship
- LU1_unemployed : unemployment

```{r}
lfs_micro_subset <-
  lfs_micro_arm_2020 %>%
  select(id_hh,id_indiv,B5,B6,B3,A3,B11,B7,E15,C2,LU1_unemployed,WeightsCalib_year) %>% 
  mutate(
    dob = paste0(B5,"_",B6), # date of birth
    LU1_unemployed = as.factor(ifelse(is.na(LU1_unemployed),0,1)) 
         ) %>% 
  select(-B5,-B6)
```


### A simple way to apply PRAM

```{r}
pram_1 <- pram(
  lfs_micro_subset,
  variables = "LU1_unemployed"
)

str(pram_1,1) # It is not a sdc Micro object, list of variables xwith attributes

attributes(pram_1)
attr(pram_1,"summary")
attr(pram_1,"pram_params")

# build data based on the results
data_pram <- 
  do.call(cbind,pram_1) %>%
  data.frame()

# Original count
data_pram %>% 
  group_by(LU1_unemployed) %>% 
  count()

# the modify variable is suffixed by "_pram"
data_pram %>% 
  group_by(LU1_unemployed_pram) %>% 
  count()

data_pram %>% 
  group_by(LU1_unemployed,LU1_unemployed_pram) %>% 
  count() %>% 
  ungroup() %>% 
  pivot_wider(
    names_from = LU1_unemployed_pram,
    values_from = n
    )
```

### Define the pram parameters  

```{r}



```

### How to perform stratification ?

regarder si on peut mettre 2 matrices différentes pour ces sous groupes ...
```{r}
res_strata <- pram(
  obj = lfs_micro_subset,
  variables = "LU1_unemployed",
  strata_variables = c("B3")
  )

?pram

attr(res_strata,"pram_params")
```

### How to measure the information loss ?
```{r}


```



### Applying PRAM on a SDC_micro_obj 

Prepare the sdc micro object
```{r}
selectedKeyVars = c('dob','A3','B3','B7','B11')

# weight variable
selectedWeightVar = c('WeightsCalib_year')

# selected pram variables
selectedPramVars = c('LU1_unemployed')

# household id variable (cluster)
selectedHouseholdID = c('id_hh')

sdcInitial <- createSdcObj(
  dat = lfs_micro_subset,
  keyVars     = selectedKeyVars,
  weightVar   = selectedWeightVar,
  pramVars    = selectedPramVars,
  hhId        = selectedHouseholdID,
  seed = 12345
)

str(sdcInitial,2)
```

```{r}

pram_2  <- pram(sdcInitial,variables = NULL,strata_variables = NULL)
str(pram_2,1)
# If argument 'variables' is NULL, all variables from slot 'pramVars' will be used if possible.

pram_2@origData %>%
  group_by(LU1_unemployed) %>%
  count()

# PRAM count 
pram_2@manipPramVars %>%
  group_by(LU1_unemployed) %>%
  count()

# What happens ?
table(
  pram_2@manipPramVars$LU1_unemployed,
  pram_2@origData$LU1_unemployed
  )

```

Which parameters has been used by default ?
```{r}

sdcInitial@pram
pram_2@pram

# P Matrix
pram_2@pram$params$LU1_unemployed$Rs

# Transitions
pram_2@pram$transitions$LU1_unemployed

```













### Test on 2014
```{r}
# https://www.armstat.am/en/?nid=212
download.file(
  destfile = "data/lfs_micro_arm_2014.7z",
  url = "https://www.armstat.am/file/doc/99495978.7z"
)

archive::archive_extract("data/lfs_micro_arm_2014.7z",dir = "data/")
# To read it 
lfs_micro_arm_2014 <- haven::read_spss("data/LFS_Micro data 2014.sav")
lfs_micro_arm_2014 %>% group_by(D15) %>% count()
# few answer.. again
```


###To DO
- strata -> double matirices possible ?
- Regarder SUDA 
- Test données synthétiques

