---
title: "Synthdata"
output: html_document
date: '2022-05-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
packs <- c("xlsx","dplyr","tidyr","sdcMicro","archive","synthpop","ggplot2","simPop")
p <- sapply(packs, install.packages)
p <- lapply(packs,function(p) suppressPackageStartupMessages(library(p,character.only = TRUE)))
rm(p)
# rm(list=ls())
```

### Prepare data :

```{r}

download.file(
  destfile = "data/lfs_micro_arm_2020.7z",
  url = "https://www.armstat.am/file/doc/99528268.7z"
)
archive::archive_extract("data/lfs_micro_arm_2020.7z",dir = "data/")
# To read it 
lfs_micro_arm_2020 <- haven::read_spss("data/LFS_2020_2020 Dataset_Residents.sav")

lfs_micro_arm_2020 <-
  lfs_micro_arm_2020 %>% 
  mutate(
    id_hh = as.numeric(substr(IDmem,1,nchar(IDmem)-2)), # concatenation of month + questionnaire_num
    id_indiv = substr(IDmem,nchar(IDmem)-1,nchar(IDmem))
  ) 

lfs_micro_subset <-
  lfs_micro_arm_2020 %>%
  select(id_hh,id_indiv,B5,B6,Age,B3,A3,B11,B7,E15,C2,LU1_unemployed,WeightsCalib_year) %>% 
  mutate(
    dob = paste0(B5,"_",B6), # date of birth
    LU1_unemployed = as.factor(ifelse(is.na(LU1_unemployed),0,1)) 
         ) %>% 
  select(-B5,-B6)
```

### simPop

```{r}

set.seed(1234)
lfs_micro_subset <-
  lfs_micro_subset %>% 
    left_join(
      lfs_micro_subset %>% 
        group_by(id_hh) %>% 
        summarise(size = n()),
      by ="id_hh"
    )

input <- specifyInput(
                    lfs_micro_subset %>% mutate(
                      A3 = as.factor(A3),
                      Age = as.factor(Age),
                      C2 = as.factor(C2)
                      ),
                    hhid = "id_hh", # household id
                    hhsize = "size",# household size
                    strata = "A3", # regions -> the models are computed for each strata
                    weight = "WeightsCalib_year"
                    ) # sampling weight

str(input,2)
attributes(inp)$data
attr(input,"data")

```


Quasi-identifying variables :

- B5, B6 : Date of birth
- B3 : Gender
- A3 : Geographical Area (Marz)
- B11 : Marital Status 
- B7 : Diploma

Sensitive variables 

- E15 : Income
- C2 : country of citizenship
- LU1_unemployed : unemployment


1 st step, create a population with the same structure than the original one, on "basic variables"
```{r}
synthP <- simStructure(
                       data = input, 
                       method = "direct",
                       basicHHvars = c("B3", "Age", "A3")
                       )

initdata <- synthP@sample@data # initial data (n indiv =sum of weight)
genpop <- synthP@pop@data # the generated population

# by size
genpop %>%
  group_by(size) %>%
  count()

initdata %>% 
  group_by(size) %>% 
  summarise(n = sum(WeightsCalib_year))

# by Gender  x Age
genpop %>% 
  group_by(B3,Age) %>% 
  count()

initdata %>% 
  group_by(B3,Age) %>% 
  summarise(n = sum(WeightsCalib_year))
```
Step 2 : add categorica variables simulate by multinomial model
```{r}
synthP <- simCategorical(
  synthP, 
  additional = c("B11", "B7", "C2"),
  method = "multinom",
  nr_cpus = 4
  )

genpop <- synthP@pop@data

# Marital Status
genpop %>% 
  group_by(B11) %>% 
  count()

initdata %>% 
  group_by(B11) %>% 
  summarise(n = sum(WeightsCalib_year))

# Diploma
genpop %>% 
  group_by(B7) %>% 
  count()

initdata %>% 
  group_by(B7) %>% 
  summarise(n = sum(WeightsCalib_year))

# citizenship
genpop %>% 
  group_by(C2) %>% 
  count()

initdata %>% 
  group_by(C2) %>% 
  summarise(n = sum(WeightsCalib_year))

# SimRelation function permit to take into account the fact that peple leave in the same household => no infepedance
```

### How to measure information loss ?

```{r}
tab <- spTable(synthP,select = c("B3","A3")) # cal
str(tab,2) # calculate the expected cross tabulation an the created incross tabulation ion synthpop 

spMosaic(tab, labeling = labeling_border(abbreviate = c(A3 = TRUE)))

```
```{r}
spCdfplot(synthP,"Age",cond = "B3", layout = c(1,2))

```